%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Platform Engineer (Contract)} % Job title
    {Woven by Toyota (Tokyo, Japan)} % Organization
    {Jan. 2026 - Present} % Location
    {Jan. 2026 - Present} % Date(s)
    { 
      \begin{cvitems}
        \item {Architected a Python interpreter resolution policy for 4,000+ developers across multiple Toyota group companies working within heterogeneous monorepos (Bazel, Poetry, ad-hoc scripts) in the AD/ADAS domain. Enforced this by implementing a sane-default resolution layer that decoupled Python from OS upgrade lifecycles to unblock global OS migrations with minimal developer disruption.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Infrastructure Engineer} % Job title
    {Rakuten Group, Inc. (Tokyo, Japan)} % Organization
    {Apr. 2023 - Jan. 2026} % Location
    {Jan. 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Selected for merit-based promotion to Grade A (P4 / Senior Level) following the 2025 year-end performance review in recognition of leadership in the hardware lab and decommissioning projects.}
      \end{cvitems}
    }
  
  \cventry
    {Infrastructure Engineer} % Job title
    {} % Organization
    {} % Location
    {Jan. 2025 - Dec. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Spearheaded the 0-to-1 development of an isolated hardware lab for pre-purchase benchmarking; 
        succeeded the project's Principal Engineer as Lead Designer and Owner,
        taking full responsibility for architectural evolution, procurement strategy, and automated testing.}
        \item {Architected and implemented an end-to-end standardized server decommissioning workflow adopted as the current organizational standard;
        retired 5,000+ legacy servers saving millions of yen monthly and mentored a successor to ensure long-term operational continuity.}
        \item {Served as a co-owner of a 200k+ line Python/Config internal automation framework, leading its maintenance and continuous feature enhancement.
         Iteratively identified and resolved systemic bottlenecks through root-cause analysis (RCA) of complex failures, optimizing operational processes for multiple global departments.}
      \end{cvitems}
    }
  
  \cventry
    {Associate Infrastructure Engineer} % Job title
    {} % Organization
    {} % Location
    {Apr. 2023 - Dec. 2024} % Date(s)
    {
        \begin{cvitems}
        \item {Engineered and improved various automation pipelines (Python, Bash, Jenkins) to streamline the provisioning and configuration management (Chef Infra) of a 60,000+ server global Bare-Metal-as-a-Service (BMaaS) platform.}
        \item {Refactored the Python-based Chef cookbook delivery system to eliminate race conditions and non-deterministic behavior; reduced daily synchronization time by 12x (6h → 30m) while ensuring data integrity within each environment boundary.}
        \item {Significantly contributed to reducing server provisioning error rates from 30\% to 10\% by engineering automated firmware upgrades and hardware/network health-check workflows, markedly improving deployment reliability.}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Back-End Engineer (Internship)} % Job title
    {Money Forward, Inc. (Remote, Japan)} % Organization
    {Apr. 2022 - May 2022} % Location
    {Apr. 2022 - May 2022} % Date(s)
    {
        \begin{cvitems}
        \item {Implemented circuit-breaker pattern in a Go microservice to enhance resilience and prevent cascading failures, ensuring service availability.}
        \end{cvitems}
    }


%---------------------------------------------------------
% \cventry
%   {Study Assistant} % Job title
%   {Kwansei Gakuin University} % Organization
%   {Japan} % Location
%   {Apr. 2021 - Sep. 2021} % Date(s)
%   {
%       AI Training Program Teaching Assistant: Facilitated student understanding of API architecture and development environments, promoting technical fluency.
%   }
%---------------------------------------------------------
  % \cventry
  %   {Mathematics Teacher (Part-Time)} % Job title
  %   {Osaka International School of Culture and Language (OBKG)} % Organization
  %   {Osaka, Japan} % Location
  %   {Feb. 2021 - Nov. 2021} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Taught a class of international students math for the Japanese university admission exam.}
  %       \item {Designed curriculum from scratch, with special attention to peculiarities of Japanese math notation.}
  %       \item {Average score improved by 10\%, highest score improved by 20\% compared to last year.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
