%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Associate System Infrastructure Engineer (Permanent)} % Job title
    {Rakuten Group, Inc.} % Organization
    {Tokyo, Japan} % Location
    {Apr. 2023 - Present} % Date(s)
    {
      \begin{cvjobdesc} % Description(s) of tasks/responsibilities
        I am a member of the DevOps team that provides mission-critical Bare Metal as a Service (BMaaS) within a private cloud. This service, in turn, serves as the foundation for other cloud services such as LBaaS and CaaS. My daily tasks involve creating automation pipelines and maintaining the orchestration of necessary services to deliver this service.
        \vspace{2.0mm}
        \\Responsibilities:
        \begin{cvbullets}
        \item {Maintain and troubleshoot the provisioning of tens of thousands of Linux-based compute resources using a mix of in-house tools and external solutions like Chef Infra.}
        \item {Architect and implement automation pipelines using Python, Bash, and Ruby scripting alongside CI/CD tools like Jenkins.}
        \item {Collaborate effectively not only within the Japan team, comprised of members from different countries, but also with overseas teams in completely different time zones.}
        \end{cvbullets}
        \vspace{2.0mm}
        Key Projects:
        \begin{cvbullets}
        \item {End-to-end implementation of firmware upgrade standardization and automation.}
        \item {Streamlining the verification pipeline for the server recycle process.}
        \end{cvbullets}
      \end{cvjobdesc}
    }

% %---------------------------------------------------------
%   \cventry
%     {Back-End Engineer (Internship)} % Job title
%     {Money Forward, Inc.} % Organization
%     {Remote, Japan} % Location
%     {Apr. 2022 - May 2022} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Developed circuit-breaker feature for an internal microservice}
%       \end{cvitems}
%     }

%---------------------------------------------------------
  \cventry
    {Mathematics Teacher (Part-Time)} % Job title
    {Osaka International School of Culture and Language (OBKG)} % Organization
    {Osaka, Japan} % Location
    {Feb. 2021 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught a class of international students math for the Japanese university admission exam.}
        \item {Designed curriculum from scratch, with special attention to peculiarities of Japanese math notation.}
        \item {Average score improved by 10\%, highest score improved by 20\% compared to last year.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
